### 2018-07-23 express2018/formal.tex
Clarified 'Getting a glimpse of user involvement in proving the theorems mentioned in Section 5. Is HOL able to prove the theorems automatically, or is it an interactive process?' #43

HOL4 is written in Standard ML, a single programming language who
plays three different roles: (The situation is quite different in
other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item it is used to implement tactics (and tacticals) for writing proofs;
\item it is used as the command language of the HOL interactive shell.
\end{enumerate}
\hl{Moreover, using} the same language HOL4 users can write complex automatic
verification tools by calling HOL's interactive theorem proving facilities.

>>>>

HOL4 is written in Standard ML, a single programming language who
plays three different roles:
%(The situation is quite different in other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item it is used to implement tactics (and tacticals) for writing proofs;
\item it is used as the command language of the HOL interactive shell.
\end{enumerate}
\hl{Moreover, using} the same language HOL4 users can write complex automatic
verification tools by calling HOL's interactive theorem proving
facilities. \hl{(The formal proof of theorems in CCS theory
is mostly done by an \emph{interactive process} closely following
their informal proofs.)}
